Make any stupid plot you want

### 2021-01-20 draft/sections/math.tex
sections

\subsubsection{Variables: Fiber Space $F$}
\label{sec:data_fiber}
The fiber is a topological space containing the set of all records that could possibly be in the dataset, even values that do not actually exist in the dataset. For example, a fiber $F$ that is the temperature variable from GHCN is the range of physically possible temperature values $ U_{temp} = \{x \in \mathbb{R}^+\}$. 
\begin{equation}
    F = U_{temp}
\end{equation}
Then lets add the time variable from GHCN $U_{time} = \{x \in \mathbb({Z}^+ \mid x \geq 1011832\}$ 
\begin{equation}
F =  U_{temp} \times U_{time}
\end{equation}
such that $F$ is the cartesian product of $F_0=U_{temp}$ and $F_1 = U_{time}$. The elements in a given fiber set do not need to be scalers; for example the location of each record can be encoded as $U_{loc} = \{y, x \in \mathbb{R}^{2} \mid -90 \leq y \leq 90, -180 \leq x -180\}$: 
\begin{equation}
    F = U_{temp} \times U_{time} \times U_{loc}
\end{equation}
such that one record $r$ in the fiber would have the form $(temperature,\, time,\, (latitude,\, longitude))$. We also add the variable name and measurement scale $M$ monoid actions to the fiber $F_i$ such that 
\begin{align}
    F_0 &= (\textit{temperature},\, U_{temp},\, M_0)\\
    F_1 &= (\textit{time},\, U_{time},\, M_1)\\
    F_2 &= (\textit{location},\, U_{loc},\, M_2)
\end{align}
 or more generally (name, type, monoid action)
 \begin{equation}
    F_i = (\textit{name},\, U_{type},\, M_{i})
 \end{equation}
where type is the set of values defined by the datatype as described in Spivak's categorical formulation of databases \cite{spivakSIMPLICIALDATABASES}. We describe $M$ in more detail in section~\ref{sec:data_monoid}. We can keep growing the fiber
\begin{equation}
F= F_{0} \times \ldots \times F_{i}\times\ldots\times F_{n}
\end{equation}
and identify the elements in the record by the variable name. We will often be working with the decoupled fiber $F_i$ rather than the total fiber $F$.

@@

A fiber bundle is trivial if $E = K\times F$, which means that the fibers $F$ are the same over every $k$. We can make many non-trivial spaces locally trivial by breaking up the total space $E$ over local neighborhoods $U \subset K$ such that the fibers are equivalant. An example of a non-trivial fiber bundle is a mobius strip, where because of the twist some fibers are $\left[0,1\right]$ and others are $\left[1,0\right]$ such that we cannot construct a global map of which edge is 0 and which edge is 1.  In figure ~\ref{fig:data_base_transition}, the mobius strip is cut into two rectangular base spaces over $K=\{e_1, e_2\}$. We define transition functions from the fiber to the fiber along the edges of the rectangles such that we can glue these rectangles together to reform the mobius strip. A constraint we impose on the transition functions is that the monoid actions are commutative
-% need more detail please on commutativty

@@

\subsubsection{Values: Sections $\tau$}
\label{sec:data_section}
%%maybe pull down/redo figure
%%% visual variable encoding in a consistent/atomic way in a complex structure 
\label{sec:section_data}
The sections of the fiber bundles are the instances of the data. They are the functions that map from a point $k \in K$ to a set of values in $F$. For example, if we have a database, the section is the table that yields a row given an index. The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}
such that %%insrt math equiality here 
%%% change to b\c locally trivial, can represent 
If the fiber bundle is trivial, then $E = K \times F$ \cite{rowlandFiberBundle,FiberBundle2020}:
\begin{equation}
    \label{eq:section_return}
    \tau(k) = (k, (x_{F_{0}}, \ldots, x_{F_{n}}))
\end{equation}
which is also true when the fiber bundle is locally trivial over $U \subset K$.
%%%can decompose bundles into Ei such that \tau: E_{i} \rightarrow K, where F_{i} is the fiber of E_{i}
which we can also decompose such that
\begin{align}
\tau_{0}(k) &= (k, (x_{F_{0}}))\\
            & \vdotswithin{=}\\
\tau_{n}(k) &= (k, (x_{F_{n}}))
\end{align}

>>>>

\subsubsection{Variables: Fiber Space $F$}
\label{sec:data_fiber}
The fiber is a topological space containing the set of all records that could possibly be in the dataset, even values that do not actually exist in the dataset. For example, a fiber $F$ that is the temperature variable from GHCN is the range of physically possible temperature values $ U_{temp} = \{x \in \mathbb{R}^+\}$. 
\begin{equation}
    F = U_{temp}
\end{equation}
Then lets add the time variable from GHCN $U_{time} = \{x \in \mathbb({Z}^+ \mid x \geq 1011832\}$ 
\begin{equation}
F =  U_{temp} \times U_{time}
\end{equation}
such that $F$ is the cartesian product of $F_0=U_{temp}$ and $F_1 = U_{time}$. The elements in a given fiber set do not need to be scalers; for example the location of each record can be encoded as $U_{loc} = \{y, x \in \mathbb{R}^{2} \mid -90 \leq y \leq 90, -180 \leq x -180\}$: 
\begin{equation}
    F = U_{temp} \times U_{time} \times U_{loc}
\end{equation}
such that one record $r$ in the fiber would have the form $r=(temperature,\, time,\, (latitude,\, longitude))$. We also add the variable name and measurement scale $M$ monoid actions to the fiber $F_i$ such that 
\begin{align}
    F_0 &= (\textit{temperature},\, U_{temp},\, M_0)\\
    F_1 &= (\textit{time},\, U_{time},\, M_1)\\
    F_2 &= (\textit{location},\, U_{loc},\, M_2)
\end{align}
 or more generally (name, type, monoid action)
 \begin{equation}
    F_i = (\textit{name},\, U_{type},\, M_{i})
 \end{equation}
where type is the set of values defined by the datatype as described in Spivak's categorical formulation of databases \cite{spivakSIMPLICIALDATABASES}. We describe $M$ in more detail in section~\ref{sec:data_monoid}. We can keep growing the fiber
\begin{equation}
F= F_{0} \times \ldots \times F_{i}\times\ldots\times F_{n}
\end{equation}
and identify the elements in the record by the variable name. We will often be working with the decoupled fiber $F_i$ rather than the total fiber $F$.

@@

A fiber bundle is trivial if $E = K\times F$, which means that the fibers $F$ are the same over every $k$ \cite{rowlandFiberBundle,FiberBundle2020}. We can make many non-trivial spaces locally trivial by breaking up the total space $E$ over local neighborhoods $U \subset K$ such that the fibers are equivalant. An example of a non-trivial fiber bundle is a mobius strip, where because of the twist some fibers are $\left[0,1\right]$ and others are $\left[1,0\right]$ such that we cannot construct a global map of which edge is 0 and which edge is 1.  In figure ~\ref{fig:data_base_transition}, the mobius strip is cut into two rectangular base spaces over $K=\{e_1, e_2\}$. We define transition functions from the fiber to the fiber along the edges of the rectangles such that we can glue these rectangles together to reform the mobius strip. A constraint we impose on the transition functions is that the monoid actions are commutative
-% need more detail please on commutativty

@@

\subsubsection{Values: Sections $\tau$}
\label{sec:data_section}
\begin{figure}[ht!]
    \label{fig:base_space_div}
    \includegraphics[width=.5\linewidth]{figures/math/k_qspace.png}
    \caption{ A section $\tau$ is a mapping from $K$ to $F$ that returns a record for each $k \in K$.}
\end{figure}

The sections of the fiber bundle are maps from points $k$ on $K$ to records $r$ in $F$. When we map our data to visual variables, the $\tau$ returns the set of values that are mapped together into a single graphic element. For GHCN, the $\tau$ functions return a table in a database with the schema defined in $F$ and the connectivity defined in $K$: this means the sections can be defined such that all values have the same year or location, e.g each table returned by a $\tau$ is for a different station.

The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}
such that %%insrt math equiality here 
%%% change to b\c locally trivial, can represent 
If the fiber bundle is trivial, then :
\begin{equation}
    \label{eq:section_return}
    \tau(k) = (k, (x_{F_{0}}, \ldots, x_{F_{n}}))
\end{equation}
which is also true when the fiber bundle is locally trivial over $U \subset K$.
%%%can decompose bundles into Ei such that \tau: E_{i} \rightarrow K, where F_{i} is the fiber of E_{i}
which we can also decompose such that
\begin{align}
\tau_{0}(k) &= (k, (x_{F_{0}}))\\
            & \vdotswithin{=}\\
\tau_{n}(k) &= (k, (x_{F_{n}}))
\end{align}
